Simulation Study: Unimodal Settings (t-11)

### 2018-09-06 datasets/simulations/simulations-uasettings.Rmd
Fix relative path of R directory for suppl Rmds; change ua output file names

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-benchmark-bimodal.rds")

>>>>

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-benchmark-bimodal.rds")

### 2018-09-06 datasets/simulations/supplementary/simulations-uasettings-originalscale.Rmd
Fix relative path of R directory for suppl Rmds; change ua output file names

---
title: "Simulation Study: Varying Effect Size"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-benchmark-bimodal.rds")

>>>>

---
title: "Simulation Study: Unimodal Settings"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## load helper functions
for (f in list.files("../../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-benchmark-bimodal.rds")

### 2018-09-06 datasets/simulations/supplementary/simulations-uasettings-t-originalscale.Rmd
Fix relative path of R directory for suppl Rmds; change ua output file names

---
title: "Simulation Study: Varying Effect Size (t-11)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`. This set of simulations is similar to those
presented in `simulations-varyingeffectsize.Rmd`, however, t-distributed test
statistics are used.

>>>>

---
title: "Simulation Study: Unimodal Settings (t-11)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`. This set of simulations is similar to those
presented in `simulations-uasettings-originalscale.Rmd`, however, t-distributed test
statistics are used.
